---
title: "Individual Effect Size"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(metafor)
library(dmetar)
library(esc)
library(dplyr)
library(tidyverse)
library(meta)
library(ggplot2)
library(metasens)
library(numDeriv)
```

## Raw data 

control will always be group 1 in SMD calculation. this was manually switched in the imported cvs  


Study 1 

bagagiolo_2022 - still looking for full text, emailed corresponding author

ODDI score 

Treatment 
Control with LLT 

```{r}

# PP @ 3 months

esc_2x2(grp1yes = 23, grp1no = 22,
              grp2yes = 3, grp2no = 41,
              es.type = "g")

# # ITT @ 3 months
# esc_2x2(grp1yes = 3, grp1no = 45,
#               grp2yes = 23, grp2no = 25,
#               es.type = "g")
# 
# # PP @ 1 year
# esc_2x2(grp1yes = 5, grp1no = 31,
#               grp2yes = 28, grp2no = 13,
#               es.type = "g")
# 
# # ITT @ 1 year
# esc_2x2(grp1yes = 5, grp1no = 43,
#               grp2yes = 28, grp2no = 20,
#               es.type = "g")
# 
# # ITT @ 3 months 
# 
# ### Normal 
# 
# esc_2x2(grp1yes = 3, grp1no = 45,
#               grp2yes = 23, grp2no = 25,
#               es.type = "g")
# 
# ### Mild 
# 
# esc_2x2(grp1yes = 24, grp1no = 24,
#               grp2yes = 16, grp2no = 32,
#               es.type = "g")
# 
# ### Moderate 
# 
# esc_2x2(grp1yes = 16, grp1no = 32,
#               grp2yes = 28, grp2no = 20,
#               es.type = "g")
# 
# ### Severe
# 
# esc_2x2(grp1yes = 5, grp1no = 43,
#               grp2yes = 1, grp2no = 47,
#               es.type = "g")
# 
# # PP @ 3 months 
# 
# ### Normal 
# 
# esc_2x2(grp1yes = 3, grp1no = 33,
#               grp2yes = 20, grp2no = 21,
#               es.type = "g")
# 
# ### Mild 
# 
# esc_2x2(grp1yes = 18, grp1no = 18,
#               grp2yes = 12, grp2no = 29,
#               es.type = "g")
# 
# ### Moderate 
# 
# esc_2x2(grp1yes =13, grp1no = 23,
#               grp2yes = 10, grp2no = 31,
#               es.type = "g")
# 
# ### Severe
# 
# esc_2x2(grp1yes = 2, grp1no = 34,
#               grp2yes = 14, grp2no = 27,
#               es.type = "g")
# 
# # ITT @ 12 months 
# 
# ### Normal 
# 
# esc_2x2(grp1yes = 5, grp1no = 43,
#               grp2yes = 28, grp2no = 20,
#               es.type = "g")
# 
# ### Mild 
# 
# esc_2x2(grp1yes = 35, grp1no = 13,
#               grp2yes = 16, grp2no = 32,
#               es.type = "g")
# 
# ### Moderate 
# 
# esc_2x2(grp1yes = 6, grp1no = 42,
#               grp2yes = 2, grp2no = 46,
#               es.type = "g")
# 
# ### Severe
# 
# esc_2x2(grp1yes = 2, grp1no = 46,
#               grp2yes = 2, grp2no = 46,
#               es.type = "g")
# 
# # PP @ 12 months 
# 
# ### Normal 
# 
# esc_2x2(grp1yes = 5, grp1no = 31,
#               grp2yes = 28, grp2no = 13,
#               es.type = "g")
# 
# ### Mild 
# 
# esc_2x2(grp1yes = 23, grp1no = 13,
#               grp2yes = 9, grp2no = 32,
#               es.type = "g")
# 
# ### Moderate 
# 
# esc_2x2(grp1yes = 6, grp1no = 30,
#               grp2yes = 2, grp2no = 39,
#               es.type = "g")
# 
# ### Severe
# 
# esc_2x2(grp1yes = 2, grp1no = 34,
#               grp2yes = 2, grp2no = 39,
#               es.type = "g")

```


Study 2 

castro-sanchez_2010

impression of improvement and impression of severity scales used as outcomes. Most wideling applicable i.e. validated 

perhaps should only select a single timepoint?

(1) between group calc @ post treatment (20 weeks) 
(2) between group calc @ 2 months post treatment 
(3) between group calc @ 1 year post treatment 
(4) conversion to Hedge's g 

```{r}

##create 2 dataframes to hold results

# identifier = c("pt1_IG", "pt1_PG", "pt2_IG", "pt2_PG", "pt3_IG", "pt3_PG")
# 
# cgi_i_n_ig = c(46, 46, 46)
# 
# cgi_i_mean_ig = c(5.02, 5.99, 6.14)
# 
# cgi_i_sd_ig = c(0.76, 0.88, 0.80)
# 
# cgi_i_n_pg = c(46, 46, 46)
# 
# cgi_i_mean_pg = c(6.20, 6.30, 6.43)
# 
# cgi_i_sd_pg = c(0.89, 0.65, 0.72)
# 
# cgi_i = data.frame(identifier, cgi_i_n_ig, cgi_i_mean_ig, cgi_i_sd_ig, cgi_i_n_pg, cgi_i_mean_pg, cgi_i_sd_pg)
# 
# 
# cgi_s_n_ig = c(46, 46, 46)
# 
# cgi_s_mean_ig = c(5.68, 5.79, 5.96)
# 
# cgi_s_sd_ig = c(0.89, 3.31, 2.15)
# 
# cgi_s_n_pg = c(46, 46, 46)
# 
# cgi_s_mean_pg = c(6.00, 5.98, 6.12)
# 
# cgi_s_sd_pg = c(1.04, 5.80, 3.97)
# 
# cgi_s = data.frame(identifier, cgi_s_n_ig, cgi_s_mean_ig, cgi_s_sd_ig, cgi_s_n_pg, cgi_s_mean_pg, cgi_s_sd_pg)
# 
# ## effect size for cgi_i
# 
# es_cgi_i = c()
# 
# for ( i in seq(1,3)) {
#   es_cgi_i[[i]] = esc_mean_sd(grp1m = cgi_i$cgi_i_mean_pg[i], 
#                            grp2m = cgi_i$cgi_i_mean_ig[i], 
#                            grp1sd = cgi_i$cgi_i_sd_pg[i], 
#                            grp2sd = cgi_i$cgi_i_sd_ig[i], 
#                            grp1n = cgi_i$cgi_i_n_pg[i], 
#                            grp2n = cgi_i$cgi_i_n_ig[i], es.type = "g")
# 
# }
# 
# ## effect size for cgi_s
# 
# es_cgi_s = c()
# 
# for ( i in seq(1,3)) {
#   es_cgi_s[[i]] = esc_mean_sd(grp1m = cgi_s$cgi_s_mean_pg[i], 
#                            grp2m = cgi_s$cgi_s_mean_ig[i], 
#                            grp1sd = cgi_s$cgi_s_sd_pg[i], 
#                            grp2sd = cgi_s$cgi_s_sd_ig[i], 
#                            grp1n = cgi_s$cgi_s_n_pg[i], 
#                            grp2n = cgi_s$cgi_s_n_ig[i], es.type = "g")
# 
# }
# 
# ## correct to g 
# 
# 
# cgi_i_g = c()
# 
# for (i in seq(1,3)){
#   cgi_i_g[i] = hedges_g(es_cgi_i[[i]][1], 46)
# 
# }
# 
# 
# cgi_s_g = c()
# 
# for (i in seq(1,3)){
#   cgi_s_g[i] = hedges_g(es_cgi_s[[i]][1], 46)
# 
# }


esc_mean_sd(grp1m = 5.12, 
            grp2m = 3.12, 
            grp1sd = 3.03, 
            grp2sd = 2.22, 
            grp1n = 32, 
            grp2n = 32, es.type = "g")

```

ducan_2008

(1) import 
(2) between group effect
(3) convert to hedges g 

```{r}

duncan_2008 = read.delim("clipboard")

## effect size 

duncan_effect = c()

for ( i in seq(1,length(duncan_2008[[1]]))) {
  duncan_effect[[i]] = esc_mean_sd(grp1m = duncan_2008$OMT.Mean[i], 
                                  grp2m = duncan_2008$Control.mean[i], 
                                  grp1sd = duncan_2008$OMT.Std[i], 
                                  grp2sd = duncan_2008$Control.Std[i], 
                                  grp1n = duncan_2008$OMT.Sample[i], 
                                  grp2n = duncan_2008$Control.Sample[i], es.type = "g")

}

out <- data.frame(matrix(ncol = 5, nrow = length(duncan_effect)))

for (i in seq(1, length(duncan_effect))){
  
  mid <- data.frame( "ES" = duncan_effect[[i]]$es, "SE" = duncan_effect[[i]]$se, "VAR" = duncan_effect[[i]]$var, "CI_LO" = duncan_effect[[i]]$ci.lo, "CI_HI" = duncan_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

out

```

elden_2013

```{r}

# elden_2013 = read.delim("clipboard")

## effect size 

elden_effect = c()

for ( i in seq(1,length(elden_2013[[1]]))) {
  elden_effect[[i]] = esc_mean_sd(grp1m = elden_2013$Control.mean[i], 
                                  grp2m = elden_2013$OMT.Mean[i], 
                                  grp1sd = elden_2013$Control.Std[i], 
                                  grp2sd = elden_2013$OMT.Std[i], 
                                  grp1n = elden_2013$Control.Sample[i], 
                                  grp2n = elden_2013$OMT.Sample[i], es.type = "g")
}

for (i in seq(1, length(elden_effect))){
  
  mid <- data.frame( "ES" = elden_effect[[i]]$es, "SE" = elden_effect[[i]]$se, "VAR" = elden_effect[[i]]$var, "CI_LO" = elden_effect[[i]]$ci.lo, "CI_HI" = elden_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}
```


haller_2016

```{r}

# haller_2016 = read.delim("clipboard")

## effect size 

haller_effect_t1 = c()

for ( i in seq(1,length(haller_2016[[1]]))) {
  haller_effect_t1[[i]] = esc_mean_sd(grp1m = haller_2016$Control.mean[i], 
                                  grp2m = haller_2016$OMT.Mean[i], 
                                  grp1sd = haller_2016$Control.Std[i], 
                                  grp2sd = haller_2016$OMT.Std[i], 
                                  grp1n = haller_2016$Control.Sample[i], 
                                  grp2n = haller_2016$OMT.Sample[i], es.type = "g")
}

for (i in seq(1, length(haller_effect_t1))){
  
  mid <- data.frame( "ES" = haller_effect_t1[[i]]$es, "SE" = haller_effect_t1[[i]]$se, "VAR" = haller_effect_t1[[i]]$var, "CI_LO" = haller_effect_t1[[i]]$ci.lo, "CI_HI" = haller_effect_t1[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

```




```{r}

# haller_2016_t2 = read.delim("clipboard")

## effect size 

haller_effect_t2 = c()

for ( i in seq(1,length(haller_2016_t2[[1]]))) {
  haller_effect_t2[[i]] = esc_mean_sd(grp1m = haller_2016_t2$Control.mean[i], 
                                  grp2m = haller_2016_t2$OMT.Mean[i], 
                                  grp1sd = haller_2016_t2$Control.Std[i], 
                                  grp2sd = haller_2016_t2$OMT.Std[i], 
                                  grp1n = haller_2016_t2$Control.Sample[i], 
                                  grp2n = haller_2016_t2$OMT.Sample[i], es.type = "g")
}


for (i in seq(1, length(haller_effect_t2))){
  
  mid <- data.frame( "ES" = haller_effect_t2[[i]]$es, "SE" = haller_effect_t2[[i]]$se, "VAR" = haller_effect_t2[[i]]$var, "CI_LO" = haller_effect_t2[[i]]$ci.lo, "CI_HI" = haller_effect_t2[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

```


hanten_1999

note that the two arms of this trial (resting position and CV4) were pooled  prior to effect size calculation 

alt. exclude resting position. can't find anything about it 

```{r}

# pain intensity 
# pool.groups(n1 =20,   # sample size group 1
#             n2 = 20,   # sample size group 2
#             m1 = 26.7,  # mean group 1
#             m2 = 21.6,    # mean group 2
#             sd1 = 17.3,   # sd group 1
#             sd2 = 18.1) # sd group2 

#pain affect
# pool.groups(n1 =20,   # sample size group 1
#             n2 = 20,   # sample size group 2
#             m1 = 13.0,  # mean group 1
#             m2 = 16.9,    # mean group 2
#             sd1 = 13.5,   # sd group 1
#             sd2 = 20.1) # sd group2


# hanten_1999 = read.delim("clipboard")
# 
# ## effect size 
# 
# hanten_effect = c()
# 
# for ( i in seq(1,length(hanten_1999[[1]]))) {
#   hanten_effect[[i]] = esc_mean_sd(grp1m = hanten_1999$Control.mean[i], 
#                                   grp2m = hanten_1999$OMT.Mean[i], 
#                                   grp1sd = hanten_1999$Control.Std[i], 
#                                   grp2sd = hanten_1999$OMT.Std[i], 
#                                   grp1n = hanten_1999$Control.Sample[i], 
#                                   grp2n = hanten_1999$OMT.Sample[i], es.type = "g")
# }
#intensity
esc_mean_sd(grp1m = 26.1, 
            grp2m = 21.6, 
            grp1sd = 17.3, 
            grp2sd = 18.1, 
            grp1n = 20, 
            grp2n = 20, es.type = "g")
#affect
esc_mean_sd(grp1m = 18.3, 
            grp2m = 16.9, 
            grp1sd = 20.4, 
            grp2sd = 20.1, 
            grp1n = 20, 
            grp2n = 20, es.type = "g")
```

castro-sanchez_2016

```{r}

# castro_sanchez_2016 = read.delim("clipboard")

## effect size 

castro_sanchez_effect = c()

for ( i in seq(1,length(castro_sanchez_2016[[1]]))) {
  castro_sanchez_effect[[i]] = esc_mean_sd(grp1m = castro_sanchez_2016$Control.mean[i], 
                                  grp2m = castro_sanchez_2016$OMT.Mean[i], 
                                  grp1sd = castro_sanchez_2016$Control.Std[i], 
                                  grp2sd = castro_sanchez_2016$OMT.Std[i], 
                                  grp1n = castro_sanchez_2016$Control.Sample[i], 
                                  grp2n = castro_sanchez_2016$OMT.Sample[i], es.type = "g")
}

for (i in seq(1, length(castro_sanchez_effect))){
  
  mid <- data.frame( "ES" = castro_sanchez_effect[[i]]$es, "SE" = castro_sanchez_effect[[i]]$se, "VAR" = castro_sanchez_effect[[i]]$var, "CI_LO" = castro_sanchez_effect[[i]]$ci.lo, "CI_HI" = castro_sanchez_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

```

hayden_2006 

```{r}

# hayden_2006 = read.delim("clipboard")

## effect size 

hayden_effect = c()

for ( i in seq(1,length(hayden_2006[[1]]))) {
  hayden_effect[[i]] = esc_mean_sd(grp1m = hayden_2006$Control.mean[i], 
                                  grp2m = hayden_2006$OMT.Mean[i], 
                                  grp1sd = hayden_2006$Control.Std[i], 
                                  grp2sd = hayden_2006$OMT.Std[i], 
                                  grp1n = hayden_2006$Control.Sample[i], 
                                  grp2n = hayden_2006$OMT.Sample[i], es.type = "g")
}

for (i in seq(1, length(hayden_effect))){
  
  mid <- data.frame( "ES" = hayden_effect[[i]]$es, "SE" = hayden_effect[[i]]$se, "VAR" = hayden_effect[[i]]$var, "CI_LO" = hayden_effect[[i]]$ci.lo, "CI_HI" = hayden_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

```

herzhaft_le_roy_2016

there are some weird issues with the standard deviation and confidence intervals 

```{r}

# herzhaft_le_roy_2016 = read.delim("clipboard")

## effect size 

herzhaft_le_roy_effect = c()

for ( i in seq(1,length(herzhaft_le_roy_2016[[1]]))) {
  herzhaft_le_roy_effect[[i]] = esc_mean_sd(grp1m = herzhaft_le_roy_2016$Control.mean[i], 
                                  grp2m = herzhaft_le_roy_2016$OMT.Mean[i], 
                                  grp1sd = herzhaft_le_roy_2016$Control.Std[i], 
                                  grp2sd = herzhaft_le_roy_2016$OMT.Std[i], 
                                  grp1n = herzhaft_le_roy_2016$Control.Sample[i], 
                                  grp2n = herzhaft_le_roy_2016$OMT.Sample[i], es.type = "g")
}

for (i in seq(1, length(herzhaft_le_roy_effect))){
  
  mid <- data.frame( "ES" = herzhaft_le_roy_effect[[i]]$es, "SE" = herzhaft_le_roy_effect[[i]]$se, "VAR" = herzhaft_le_roy_effect[[i]]$var, "CI_LO" = herzhaft_le_roy_effect[[i]]$ci.lo, "CI_HI" = herzhaft_le_roy_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

```

munoz_gomez_2022										

 T2 (χ2(5) =13.23, p < 0.01, CC = 0.46) and at T3 (χ2(4) = 20.14, p < 0.001, CC = 0.54)

```{r}

# munoz_gomez_2022 = read.delim("clipboard")

## effect size 

# munoz_gomez_effect = c()
# 
# for ( i in seq(1,length(munoz_gomez_2022[[1]]))) {
#   munoz_gomez_effect[[i]] = esc_mean_sd(grp1m = munoz_gomez_2022$Control.mean[i], 
#                                   grp2m = munoz_gomez_2022$OMT.Mean[i], 
#                                   grp1sd = munoz_gomez_2022$Control.Std[i], 
#                                   grp2sd = munoz_gomez_2022$OMT.Std[i], 
#                                   grp1n = munoz_gomez_2022$Control.Sample[i], 
#                                   grp2n = munoz_gomez_2022$OMT.Sample[i], es.type = "g")
#   
# }

for (i in seq(1, length(munoz_gomez_effect))){
  
  mid <- data.frame( "ES" = munoz_gomez_effect[[i]]$es, "SE" = munoz_gomez_effect[[i]]$se, "VAR" = munoz_gomez_effect[[i]]$var, "CI_LO" = munoz_gomez_effect[[i]]$ci.lo, "CI_HI" = munoz_gomez_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}


esc_chisq(chisq = 12.23,
          totaln = 50,
          es.type = "g")

esc_chisq(chisq = 20.14,
          totaln = 50,
          es.type = "g")

```

mazreati_2021										

```{r}

mazreati_2021 = read.delim("clipboard")

## effect size 

mazreati_effect = c()

for ( i in seq(1,length(mazreati_2021[[1]]))) {
  mazreati_effect[[i]] = esc_mean_sd(grp1m = mazreati_2021$Control.mean[i], 
                                  grp2m = mazreati_2021$OMT.Mean[i], 
                                  grp1sd = mazreati_2021$Control.Std[i], 
                                  grp2sd = mazreati_2021$OMT.Std[i], 
                                  grp1n = mazreati_2021$Control.Sample[i], 
                                  grp2n = mazreati_2021$OMT.Sample[i], es.type = "g")
}

for (i in seq(1, length(mazreati_effect))){
  
  mid <- data.frame( "ES" = mazreati_effect[[i]]$es, "SE" = mazreati_effect[[i]]$se, "VAR" = mazreati_effect[[i]]$var, "CI_LO" = mazreati_effect[[i]]$ci.lo, "CI_HI" = mazreati_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

```

raith_2016

```{r}

esc_mean_sd(grp1m = 20, 
            grp2m = 19, 
            grp1sd = 21.512, 
            grp2sd = 15.5814, 
            grp1n = 13, 
            grp2n = 12, es.type = "g")

esc_2x2(grp1yes = 5, grp1no = 8,
              grp2yes = 2, grp2no = 10,
              es.type = "g")

```

sandhouse_2016

```{r}
#sandhouse_2016 = read.delim("clipboard")

## effect size 

sandhouse_effect = c()

for ( i in seq(1,length(sandhouse_2016[[1]]))) {
  sandhouse_effect[[i]] = esc_mean_sd(grp1m = sandhouse_2016$Control.mean[i], 
                                  grp2m = sandhouse_2016$OMT.Mean[i], 
                                  grp1sd = sandhouse_2016$Control.Std[i], 
                                  grp2sd = sandhouse_2016$OMT.Std[i], 
                                  grp1n = sandhouse_2016$Control.Sample[i], 
                                  grp2n = sandhouse_2016$OMT.Sample[i], es.type = "g")

}

out <- data.frame(matrix(ncol = 5, nrow = length(sandhouse_effect)))
colnames(out) <- c("ES", "SE", "VAR", "CI_LO", "CI_HI")

for (i in seq(1, length(sandhouse_effect))){
  
  mid <- data.frame( "ES" = sandhouse_effect[[i]]$es, "SE" = sandhouse_effect[[i]]$se, "VAR" = sandhouse_effect[[i]]$var, "CI_LO" = sandhouse_effect[[i]]$ci.lo, "CI_HI" = sandhouse_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

out

```

sandhouse_2011

```{r}
# sandhouse_2011 = read.delim("clipboard")

## effect size 

sandhouse_effect_2011 = c()

for ( i in seq(1,length(sandhouse_2011[[1]]))) {
  sandhouse_effect_2011[[i]] = esc_mean_sd(grp1m = sandhouse_2011$Control.mean[i], 
                                  grp2m = sandhouse_2011$OMT.Mean[i], 
                                  grp1sd = sandhouse_2011$Control.Std[i], 
                                  grp2sd = sandhouse_2011$OMT.Std[i], 
                                  grp1n = sandhouse_2011$Control.Sample[i], 
                                  grp2n = sandhouse_2011$OMT.Sample[i], es.type = "g")

}

out <- data.frame(matrix(ncol = 5, nrow = length(sandhouse_effect_2011)))
colnames(out) <- c("ES", "SE", "VAR", "CI_LO", "CI_HI")

for (i in seq(1, length(sandhouse_effect_2011))){
  
  mid <- data.frame( "ES" = sandhouse_effect_2011[[i]]$es, "SE" = sandhouse_effect_2011[[i]]$se, "VAR" = sandhouse_effect_2011[[i]]$var, "CI_LO" = sandhouse_effect_2011[[i]]$ci.lo, "CI_HI" = sandhouse_effect_2011[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

out

```

terrell_2011

```{r}
# terrell_2011 = read.delim("clipboard")

## effect size 

terrell_effect = c()

for ( i in seq(1,length(terrell_2011[[1]]))) {
  terrell_effect[[i]] = esc_mean_sd(grp1m = terrell_2011$Control.mean[i], 
                                  grp2m = terrell_2011$OMT.Mean[i], 
                                  grp1sd = terrell_2011$Control.Std[i], 
                                  grp2sd = terrell_2011$OMT.Std[i], 
                                  grp1n = terrell_2011$Control.Sample[i], 
                                  grp2n = terrell_2011$OMT.Sample[i], es.type = "g")

}

out <- data.frame(matrix(ncol = 5, nrow = length(terrell_effect)))
colnames(out) <- c("ES", "SE", "VAR", "CI_LO", "CI_HI")

for (i in seq(1, length(terrell_effect))){
  
  mid <- data.frame( "ES" = terrell_effect[[i]]$es, "SE" = terrell_effect[[i]]$se, "VAR" = terrell_effect[[i]]$var, "CI_LO" = terrell_effect[[i]]$ci.lo, "CI_HI" = terrell_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

out

```

wahl_ 2008

```{r}

esc_2x2(grp1yes = 9, grp1no = 12,
              grp2yes = 9, grp2no = 14,
              es.type = "g")
```

castejon_castejon_2022

```{r}
# castejon_castejon_2022 = read.delim("clipboard")

## effect size 

castejon_castejon_effect = c()

# for ( i in seq(1,length(castejon_castejon_2022[[1]]))) {
#   castejon_castejon_effect[[i]] = esc_mean_sd(grp1m = castejon_castejon_2022$Control.mean[i], 
#                                   grp2m = castejon_castejon_2022$OMT.Mean[i], 
#                                   grp1sd = castejon_castejon_2022$Control.Std[i], 
#                                   grp2sd = castejon_castejon_2022$OMT.Std[i], 
#                                   grp1n = castejon_castejon_2022$Control.Sample[i], 
#                                   grp2n = castejon_castejon_2022$OMT.Sample[i], es.type = "g")
# 
# }

for ( i in seq(1,length(castejon_castejon_2022[[1]]))) {
  castejon_castejon_effect[[i]] = esc_mean_sd(grp1m = castejon_castejon_2022$Control.mean[i], 
                                  grp2m = castejon_castejon_2022$OMT.Mean[i], 
                                  grp1sd = castejon_castejon_2022$Control.Std[i], 
                                  grp2sd = castejon_castejon_2022$OMT.Std[i], 
                                  grp1n = castejon_castejon_2022$Control.Sample[i], 
                                  grp2n = castejon_castejon_2022$OMT.Sample[i], es.type = "g")

}

out <- data.frame(matrix(ncol = 5, nrow = length(castejon_castejon_effect)))
colnames(out) <- c("ES", "SE", "VAR", "CI_LO", "CI_HI")

for (i in seq(1, length(castejon_castejon_effect))){
  
  mid <- data.frame( "ES" = castejon_castejon_effect[[i]]$es, "SE" = castejon_castejon_effect[[i]]$se, "VAR" = castejon_castejon_effect[[i]]$var, "CI_LO" = castejon_castejon_effect[[i]]$ci.lo, "CI_HI" = castejon_castejon_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

out

```


wyatt_2011

```{r}
wyatt_2011 = read.delim("clipboard")

## effect size 

wyatt_effect = c()

for ( i in seq(1,length(wyatt_2011[[1]]))) {
  wyatt_effect[[i]] = esc_mean_sd(grp1m = wyatt_2011$Control.mean[i], 
                                  grp2m = wyatt_2011$OMT.Mean[i], 
                                  grp1sd = wyatt_2011$Control.Std[i], 
                                  grp2sd = wyatt_2011$OMT.Std[i], 
                                  grp1n = wyatt_2011$Control.Sample[i], 
                                  grp2n = wyatt_2011$OMT.Sample[i], es.type = "g")

}

out <- data.frame(matrix(ncol = 5, nrow = length(wyatt_effect)))
colnames(out) <- c("ES", "SE", "VAR", "CI_LO", "CI_HI")

for (i in seq(1, length(wyatt_effect))){
  
  mid <- data.frame( "ES" = wyatt_effect[[i]]$es, "SE" = wyatt_effect[[i]]$se, "VAR" = wyatt_effect[[i]]$var, "CI_LO" = wyatt_effect[[i]]$ci.lo, "CI_HI" = wyatt_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

out

```

mataran_penarrocha_2011

```{r}

mataran_penarrocha_2011 = read.delim("clipboard")

## effect size 

mataran_penarrocha_effect = c()

for ( i in seq(1,length(mataran_penarrocha_2011[[1]]))) {
  mataran_penarrocha_effect[[i]] = esc_mean_sd(grp1m = mataran_penarrocha_2011$Control.mean[i], 
                                  grp2m = mataran_penarrocha_2011$OMT.Mean[i], 
                                  grp1sd = mataran_penarrocha_2011$Control.Std[i], 
                                  grp2sd = mataran_penarrocha_2011$OMT.Std[i], 
                                  grp1n = mataran_penarrocha_2011$Control.Sample[i], 
                                  grp2n = mataran_penarrocha_2011$OMT.Sample[i], es.type = "g")

}

out <- data.frame(matrix(ncol = 5, nrow = length(mataran_penarrocha_effect)))
colnames(out) <- c("ES", "SE", "VAR", "CI_LO", "CI_HI")

for (i in seq(1, length(mataran_penarrocha_effect))){
  
  mid <- data.frame( "ES" = mataran_penarrocha_effect[[i]]$es, "SE" = mataran_penarrocha_effect[[i]]$se, "VAR" = mataran_penarrocha_effect[[i]]$var, "CI_LO" = mataran_penarrocha_effect[[i]]$ci.lo, "CI_HI" = mataran_penarrocha_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

out

```

cerrotelli_2013										


```{r}

esc_mean_sd(grp1m = 31.2, 
            grp2m = 26.1, 
            grp1sd = 20.2, 
            grp2sd = 16.4, 
            grp1n = 54, 
            grp2n = 47, es.type = "g")

esc_B(b = -5.906,              # unstandardized regression coefficient
      sdy = 6.939453917,       # standard deviation of predicted variable y
      grp1n = 54,              # sample size of the first group
      grp2n = 47,              # sample size of the second group
      es.type = "g")           # convert to SMD; use "g" for Hedges' g								

esc_B(b = -3.707,              # unstandardized regression coefficient
      sdy = 13.84314623,       # standard deviation of predicted variable y
      grp1n = 54,              # sample size of the first group
      grp2n = 47,              # sample size of the second group
      es.type = "g")           # convert to SMD; use "g" for Hedges' g								



```

philippi_2007										

```{r}

esc_mean_sd(grp1m = 1.2, 
            grp2m = 5.9, 
            grp1sd = 3.5, 
            grp2sd = 3.8, 
            grp1n = 16, 
            grp2n = 16, es.type = "g")

esc_mean_sd(grp1m = 13, 
            grp2m = 9.5, 
            grp1sd = 2.8, 
            grp2sd = 3.1, 
            grp1n = 16, 
            grp2n = 16, es.type = "g")



```


vandenplas_2008										

```{r}

esc_mean_sd(grp1m = 7.9, 
            grp2m = 6.5, 
            grp1sd = 6.9, 
            grp2sd = 11.1, 
            grp1n = 15, 
            grp2n = 13, es.type = "g")

esc_mean_sd(grp1m = 2.9, 
            grp2m = 5.7, 
            grp1sd = 8.8, 
            grp2sd = 9.2, 
            grp1n = 15, 
            grp2n = 13, es.type = "g")



```

vandenplas_2008										

```{r}

# Mean length of stay
esc_mean_sd(grp1m = 11.6, 
            grp2m = 9.1, 
            grp1sd = 6.7, 
            grp2sd = 2, 
            grp1n = 36, 
            grp2n = 12, es.type = "g")

# Mean length of stay - intubated neonates 
esc_mean_sd(grp1m = 10.1, 
            grp2m = 9.1, 
            grp1sd = 2.3, 
            grp2sd = 2.0, 
            grp1n = 36, 
            grp2n = 12, es.type = "g")

#median days on nasogastric tube 
esc_mean_sd(grp1m = 2.5, 
            grp2m = 2.5, 
            grp1sd = 6.9340, 
            grp2sd = 2.5969, 
            grp1n = 32, 
            grp2n = 12, es.type = "g")

# bottle feeding 

esc_2x2(grp1yes = 19, grp1no = 17,
              grp2yes = 7, grp2no = 5,
              es.type = "g")

# breastfeeing 

esc_2x2(grp1yes = 8, grp1no = 28,
              grp2yes = 2, grp2no = 10,
              es.type = "g")
# both 

esc_2x2(grp1yes = 5, grp1no = 31,
              grp2yes = 3, grp2no = 9,
              es.type = "g")

```

accorsi_2014

```{r}

#rapidity

esc_mean_sd(grp1m = 42.2, 
            grp2m = 59.2, 
            grp1sd = 7.4, 
            grp2sd = 17.6, 
            grp1n = 14, 
            grp2n = 14, es.type = "g")

#acuuracy 

esc_mean_sd(grp1m = 110.5, 
            grp2m = 116.4, 
            grp1sd = 10.5, 
            grp2sd = 24.3, 
            grp1n = 14, 
            grp2n = 14, es.type = "g")



```

rolle_2014

```{r}

rolle_2014 = read.delim("clipboard")

## effect size 

rolle_effect = c()

for ( i in seq(1,length(rolle_2014[[1]]))) {
  rolle_effect[[i]] = esc_mean_sd(grp1m = rolle_2014$Control.mean[i], 
                                  grp2m = rolle_2014$OMT.Mean[i], 
                                  grp1sd = rolle_2014$Control.Std[i], 
                                  grp2sd = rolle_2014$OMT.Std[i], 
                                  grp1n = rolle_2014$Control.Sample[i], 
                                  grp2n = rolle_2014$OMT.Sample[i], es.type = "g")
}

for (i in seq(1, length(rolle_effect))){
  
  mid <- data.frame( "ES" = rolle_effect[[i]]$es, "SE" = rolle_effect[[i]]$se, "VAR" = rolle_effect[[i]]$var, "CI_LO" = rolle_effect[[i]]$ci.lo, "CI_HI" = rolle_effect[[i]]$ci.hi)
    
  out[i,] <- mid
  
  
}

```
## Meta-analysis 

import data first

```{r}
library(readr)
Effect_Size_Data <- read_csv("Effect_Size_Data.csv")
```


Going to try a multi-level approach. 

Here I implementing a 3 level random model and then comparing with a regular 2 level model to assess performance increase. This is mostly an academic exercise. 

```{r}
full.model <- rma.mv(yi = Effect_Size_Data$TE.modified, 
                     V = Effect_Size_Data$Varience, 
                     slab = Effect_Size_Data$Author,
                     data = Effect_Size_Data,
                     mods = ~ Outcome_category,
                     random = ~ 1 | Author/es.id, 
                     test = "t", 
                     method = "REML")

full.model

removed <- rma.mv(yi = Effect_Size_Data$TE.modified, 
                     V = Effect_Size_Data$Varience, 
                     slab = Effect_Size_Data$Author,
                     data = Effect_Size_Data,
                     random = ~ 1 | Author/es.id, 
                     test = "t", 
                     method = "REML",
                     subset = !(Effect_Size_Data$Author %in% c("Castejon-Castejon et al. (2022)", "Munoz-Gomez et al. (2022)", "Mazreati et al. (2021)", "Philippi et al. (2006)")))

removed
```

```{r}
anova(full.model, removed)
```


Here I am looking at the variance explained by each level. Within study varaince is moderately low, with between is rather high indicating high heterogeneity 

```{r}

i2 <- var.comp(full.model)

summary(i2)

plot(i2)

```



Will do subgroup by risk of bias perhaps? 

```{r}
# note that risk of bias is not yet in the dataset

# subgroup.model <- rma.mv(yi = Effect_Size_Data$TE, 
#                      V = Effect_Size_Data$Varience, 
#                      slab = Effect_Size_Data$Outcome_category,
#                      data = Effect_Size_Data,
#                      random = ~ 1 | Outcome_category/es.id, 
#                      test = "t", 
#                      method = "REML",
#                      mods = ~ RoB)
# 
# 
# summary(subgroup.model)

```

Lets aggregate effects first 

```{r}

Effects <- escalc(yi = TE.modified,
                    sei = SE,
                    data = Effect_Size_Data)


#By author 

Effects.agg <- aggregate(Effects,
                           cluster = Author,
                           rho = 0.6)

#By outcome 

Effects.out.agg <- aggregate(Effects,
                           cluster = Outcome_category,
                           rho = 0.6)

```


```{r}

SE <- data.frame(matrix(ncol = 1, nrow = length(Effects.agg$vi)))

colnames(SE) <- 'SE'

for (i in seq(1, length(Effects.agg$vi))){
  
  SE$SE[i]<- sqrt(Effects.agg$vi[i])
  
}

Effects.agg['se'] <- SE


SE <- data.frame(matrix(ncol = 1, nrow = length(Effects.out.agg$vi)))

colnames(SE) <- 'SE'

for (i in seq(1, length(Effects.out.agg$vi))){
  
  SE$SE[i]<- sqrt(Effects.out.agg$vi[i])
  
}

Effects.out.agg['se'] <- SE

```



Okay lets try to pool and see what happens 

```{r}
m.gen <- metagen(TE = yi,
                 seTE = se,
                 studlab = Author,
                 data = Effects.agg,
                 sm = "g",
                 fixed = FALSE,
                 random = TRUE,
                 method.random.ci = "KR",
                 method.tau = "SJ",
                 adhoc.hakn.ci = "ci",
                 method.bias = "Thompson",
                 title = "Cranial OMM")

```



```{r}
forest.meta(m.gen, 
            sortvar = yi,
            prediction = TRUE, 
            print.tau2 = TRUE,
            leftlabs = c("Author", "g", "SE"))


```
Find outliers

```{r}
find.outliers(m.gen)

m.gen.inf <- InfluenceAnalysis(m.gen, random = TRUE)
plot(m.gen.inf, "baujat")


m.gen.ex <- metagen(TE = yi,
                 seTE = se,
                 studlab = Author,
                 data = Effects.agg,
                 sm = "g",
                 fixed = FALSE,
                 random = TRUE,
                 method.random.ci = "KR",
                 method.tau = "SJ",
                 adhoc.hakn.ci = "ci",
                 method.bias = "Thompson",
                 exclude = (Author %in% c("Castejon-Castejon et al. (2022)", "Munoz-Gomez et al. (2022)", "Mazreati et al. (2021)", "Philippi et al. (2006)")),
                 title = "Cranial OMM")


forest.meta(m.gen, 
            sortvar = yi,
            prediction = TRUE, 
            print.tau2 = TRUE,
            leftlabs = c("Author", "g", "SE"))


```

```{r}
plot(m.gen.inf, "es")
plot(m.gen.inf, "i2")
```

Testing out funnel plots. Will likely use the ones generated from the limited meta-analysis 

```{r}


col.contour = c("gray75", "gray85", "gray95")


funnel.meta(m.gen,
            xlim = c(-2, 3),
            contour = c(0.9, 0.95, 0.99),
            col.contour = col.contour,
            studlab = TRUE)
legend(x = 1.6, y = 0.01, 
       legend = c("p < 0.1", "p < 0.05", "p < 0.01"),
       fill = col.contour)


metabias(m.gen, method.bias = "Egger", plotit = TRUE)

```

Trying trimfill, will not use since it seems not very robust. This is just exploratory. 

```{r}
tf <- trimfill(m.gen)

tf.no.out <- trimfill(m.gen.ex)

summary(tf)
summary(tf.no.out)
```

Limited meta-analysis i.e. adjusting effect size for small-sample bias.

```{r}
# Create limitmeta object
lmeta <- limitmeta(m.gen)

# Funnel with curve
funnel.limitmeta(lmeta, xlim = c(-0.5, 2))

# Funnel with curve and shrunken study estimates
funnel.limitmeta(lmeta, xlim = c(-0.5, 2), shrunken = TRUE)

summary.limitmeta(lmeta)
```



Trying to play around with P value analysis. I think my data is too messy and incomplete right now


```{r}

m.gen.p <- metagen(TE = Effect_Size_Data$TE.modified,
                 seTE = Effect_Size_Data$SE,
                 studlab = Effect_Size_Data$Author,
                 data = Effect_Size_Data,
                 sm = "g",
                 fixed = FALSE,
                 random = TRUE,
                 method.random.ci = "KR",
                 method.tau = "SJ",
                 adhoc.hakn.ci = "ci",
                 method.bias = "Thompson",
                 title = "Cranial OMM")

pcurve(m.gen.p)

m.gen.pex <- metagen(TE = Effect_Size_Data$TE.modified,
                 seTE = Effect_Size_Data$SE,
                 studlab = Effect_Size_Data$Author,
                 data = Effect_Size_Data,
                 n.e = Effect_Size_Data$Experimental,
                 n.c = Effect_Size_Data$Control,
                 sm = "g",
                 fixed = FALSE,
                 random = TRUE,
                 method.random.ci = "KR",
                 method.tau = "SJ",
                 adhoc.hakn.ci = "ci",
                 method.bias = "Thompson",
                 title = "Cranial OMM",
                 subset = !(Author %in% c("Castejon-Castejon et al. (2022)", "Munoz-Gomez et al. (2022)", "Mazreati et al. (2021)", "Philippi et al. (2006)")))

pcurve(m.gen.pex)
```

```{r}
pcurve(m.gen.pex,
       effect.estimation = TRUE,
       N = m.gen.pex$n.c + m.gen.pex$n.e,
       dmin = 0,
       dmax = 2)
```






Just playing around. 
```{r}

p_values = data.frame("P" = Effect_Size_Data$Reported_P_value) 

p_values = na.omit(p_values)

p_values = p_values[p_values$P <= 0.05, ]

pp <- p_values*20 + 0.000001

pp

chi2 <- -2*sum(log(pp))
chi2

hist(p_values,
     breaks = c(0, 0.005, 0.01, 0.015, 0.02, 0.025, 0.03, 0.035, 0.04, 0.045, 0.05))

length(p_values)
k = p_values[p_values < 0.025]
length(k)


binom.test(36, 60, 0.5, alternative = 'greater')

pchisq(chi2, df = 120)

```



```{r}

m.rma <- rma(yi = Effect_Size_Data$TE.modified, 
                     vi = Effect_Size_Data$Varience, 
                     slab = Effect_Size_Data$Author,
                     data = Effect_Size_Data, 
                     test = "t", 
                     method = "REML")


s.mod = selmodel(m.rma,
         type = "halfnorm",
         steps = 0.05)





```

```{r}

summary(s.mod)
plot(s.mod)
```


```{r}
# Define the cut-points
a <- c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 
       0.65, 0.75, 0.90, 0.95, 0.99, 0.995)

# Define the selection likelihood for each interval 
# (moderate/severe selection)
w.moderate <- c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 
                0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50)
w.severe <- c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 
              0.30, 0.25, 0.10, 0.10, 0.10, 0.10)
```

```{r}
# Fit model assuming moderate selection
selmodel(m.rma, type = "stepfun", steps = a, delta = w.moderate)

# Fit model assuming severe selection
selmodel(m.rma, type = "stepfun", steps = a, delta = w.severe)
```

this should be done once the RoB is finished. 

```{r}
m.gen.reg = metareg(m.gen, ~Outcome_category)

summary(m.gen.reg)
```

